The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2013-10-09 article.tex
Improved abstract

\begin{abstract}
% Do not use inserted blank lines (ie \\) until main body of text.
\paragraph*{Background:}
Cheminformatics is a well-established field with many applications in chemistry,
drug discovery, and the life sciences. Particularly in the latter field, however,
molecular properties are not well-understood yet, and the interaction between
molecules and larger systems remains a challenge to be modeled. Therefore, the
development of new data mining and pattern recognition continues to be important
and the need for access to a cheminformatics library that one can change remains.
\paragraph*{Results:}
We here report the improvements since the 1.2 series of the Chemistry Development Kit and outline how
it evolved since the previous report. We demonstrate the new APIs we introduced
in this version and discuss the extensive quality control mechanism we have
adopted. New APIs have been introduced for substructure searching, rendering of
molecules, handling of molecular formulas, atom type perception, and InChI
support. At a quality control side we have introduced automated building,
extensive unit and use case testing, and adopted peer review.
\paragraph*{Conclusions:}
With this paper we have shown the continued effort to provide a free, Open Source
cheminformatics library, and show that such colleborative projects can survive for
a long period. We have taken advantage from the community support, and show
that an open source cheminformatics project can act as a peer reviewed
publishing platform for scientific computating software.
\end{abstract}

>>>>

\begin{abstract}
% Do not use inserted blank lines (ie \\) until main body of text.
\paragraph*{Background:}
Cheminformatics is a well-established field with many applications in chemistry,
drug discovery, and the life sciences. It provides various models to represent
chemical structures, of which the chemical graph is essential, and as such
complements quantum chemical approaches. Large scale calculations relies on
graph-based approaches, which are faster due to the graph simplification of
chemical structures. As such, cheminformatics is much used in many life
sciences fields, where the understanding of molecular properties and their
interactions with the cell and the organism. Therefore, the
development of new data mining and pattern recognition continues to be important
and the need for access to a cheminformatics library that one can change remains.
\paragraph*{Results:}
We here report the improvements of the Chemistry Development Kit since the
1.2 release series. This paper outlines how the library evolved since the
previous report. We demonstrate the new APIs we introduced
in this version and discuss the extensive quality control mechanism we have
adopted. New APIs have been introduced for substructure searching, rendering of
molecules, handling of molecular formulas, atom type perception, and InChI
support. At a quality control side we have introduced automated building,
extensive unit and use case testing, and adopted peer review.
\paragraph*{Conclusions:}
With this paper we have shown the continued effort to provide a free, Open Source
cheminformatics library, and show that such colleborative projects can survive for
a long period. We have taken advantage from the community support, and show
that an open source cheminformatics project can act as a peer reviewed
publishing platform for scientific computating software.
\end{abstract}
